Formalizing Stack Safety as a Security Property

### 2023-02-04 submission5/core.tex
CP

Stack safety properties need to describe the behavior of machine code. but they naturally
talk about function activations and stack contents---abstractions that
are (typically) not visible at machine level. To bridge this gap,
our properties are defined in terms of a {\em security semantics} layered on top of
the standard execution semantics of the machine.  This semantics identifies certain
state transitions of the machine as {\em security-relevant operations}, which update
a notional {\em security context}.  This context consists of
an (abstract) stack of function activations, each associated with a {\em view}
that maps each element of the machine state (memory location or register)
to a {\em security class} (active, sealed, etc.) which specifies how the activation
can access the element.
The action of the security-relevant operations on the context is defined by a set
of rules that depend on how the machine code makes use of the stack and registers
to implement the function abstraction.

>>>>

Stack safety properties need to describe the behavior of machine code. but they naturally
talk about function activations and stack contents---abstractions that
are typically not visible at machine level. To bridge this gap,
our properties are defined in terms of a {\em security semantics} layered on top of
the standard execution semantics of the machine.  The security semantics identifies certain
state transitions of the machine as {\em security-relevant
  operations}, which update
a notional {\em security context}.  This context consists of
an (abstract) stack of function activations, each associated with a {\em view}
that maps each element of the machine state (memory location or register)
to a {\em security class} (active, sealed, etc.) specifying how the activation
can access the element.
The action of a security-relevant operation on the context is defined by a set
of rules that describe how the machine code makes use of the stack and registers
to implement the function abstraction.
